% Sample file on how to use subfiles.
\documentclass[ExampleMasters.tex]{subfiles}

\begin{document}
\clearpage


\chapter{Software Setup (8 Seiten)}
\label{chap:software_setup}
\section{Matlab/Simulink environment}
\label{sec:matlab}

\subsection{FMI toolbox}
\subsection{dSpace RTI-blockset}
The dSpace RTI-Blockset (Real-time interface) is a plug-in for MATLAB/Simulink that allows you to connect a simulink-model to the different inputs and outputs of the MABII. There are RTI-blocks for CAN, Ethernet, LIN, FPGA and the analog and digital outputs of the MABII.
In this project only the RTI CAN MultiMessage Blockset was used. These blocks establish an interface between the physical CAN-Buses of the MABII and the simulink-model running on the MABII. There are four different blocks in this blockset: 

In the "GeneralSetup" block the paths of the model root and the destination folder for generated files are set. 

In the "ControllerSetup" block first the name of the controller has to be set, then the physical CAN-Bus, that should be used, is set by choosing a module number and a controller number. How the module- and controller numbers have to be set for the different CAN-buses of the MABII is shown in \ref{tab:CAN-layout}.
\begin{table}[h]
	\centering
	\caption{CAN-layout MABII}
	\label{tab:CAN-layout}
	\begin{tabular}{c|c|c|c|c|}
		CAN   & Module number & Controller number & ZIF-Pin CAN-High & ZIF-Pin CAN-Low  \\ \hline
		CAN1     &       1 & 1  & c2 & c3         \\
		CAN2   &      1 & 2  & b2 & b3    \\
		CAN3 &      2 & 1 & B2 & B3        \\
		CAN4& 2 & 2 & A2 & A3  \\
		CAN5& 3 & 1 & P2 & P3 \\
		CAN6& 3 & 2 & N2 & N3 \\
	\end{tabular} \\
\end{table}

After setting the module- and controller number the identifier format has to be set to either standard or extended format, the transceiver type must be chosen between ISO11898-2 and ISO11898-6. ISO11898-2 is used for a high-speed medium access unit and ISO11989-6 for the selective wake-up functionality of a high-speed medium access unit. If needed, a termination resistance of 120 Ohms can be set in the block as well. As a last step the Baud rate of the CAN-bus has to be defined.


In the "MainSetup" block a dbc-file is connected to one of the controller blocks, that were created before. A "ControllerSetup" block can only be connected to one "MainSetup" block at a time. When the dbc-file is loaded in the "MainSetup" block, the different messages and signals of the dbc-file can be chosen as inputs and/or outputs to the simulink-model.
\subsection{Volvo Truck Model}
\label{sec:VTM}
The Volvo Truck Model (VTM) is a computational framework used within Volvo Trucks to simulate the dynamic behaviours of trucks and combinations. As a library it extends Simulink, where maneuvers, track layout and the trucks kinematic and dynamic properties are linked together and then computed. This toolbox was used as a base for the simulation of the LVC including the dolly for this project. It is possible to run simulation offline with a predefined maneuver and a given environment as well online where these parameters are fed into the calculation live or as measurings from the real-world environment. For online use all relevant parameters and states can be accessed in Simulink or in case of execution on the MABII through ControlDesk as their respective representation of the Simulink variable. 

\section{ControlDesk monitoring environment}
\label{sec:control_desk}
\subsection{Maneuver control}


\subsection{Monitoring and logging}
\begin{itemize}
	\item data-format
	\item frequency
	\item synchronizing over different CANs	
\end{itemize}


\section{Arduino IDE and applications}
\label{sec:arduino_applications}

The Arduino system provides an integrated development environment (IDE)  written in Java, providing cross-platform support. It is used to develop the code as well as compiling the code and subsequently uploading it into the microcontroller via the computers serial interface. Within the IDE it is also possible to load some of the officially supported libraries directly. It conveniently is possible to monitor the serial interface as well, which is the most practical way to monitor and debug code that is executed on the Arduino. 

\begin{table}[h]
	\label{tab:list_of_arduino_libs}
	\begin{tabular}{lll}
		\textbf{Library name} & \textbf{Purpose}                                    & \textbf{Comment} \\
		LSM303                & read magnetometer on IMU via I2C                    &                \cite{lsm303_github}  \\
		L3G                   & read gyro \& accelerometer on IMU via I2C           &      
		\cite{l3g_github}            \\
		UIPethernet           &                                                     &             \cite{uip_ethernet_github}     \\
		TinyGPSPlus           & acquire and parse GPS signal from EM-506 via serial & v0.94b\cite{tiny_gps_plus_github}     \\
		mcp\_can & implement CAN via MCP2515 and MCP2551 via SPI     & \cite{mcp_can_github}
	\end{tabular}
	
	\caption{List of utilized libraries on the Arduino platform}
\end{table}

\end{document}
